Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-08 ms.tex
adjusting caption

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} Average nuclear X-ray luminosity, $\langle
  L_X \rangle = \epsilon_X \Mdot c^2$, as a function of SMBH mass.
  Black lines show our prediction in the case of heating due to the
  average SFH for galaxies corresponding to each
  black hole mass (Fig.~\ref{fig:bh_growth}), calculated using a
  power-law fit for the relationship $\Gamma(M_{\bullet})$ derived
  from the \citet{LauerFaber+:2007a} sample.  Shown for comparison are
  the measurements ({\it red stars}) and upper limits ({\it red
    triangles}) for $L_X/L_{\rm edd}$ values, from the
  \citet{Miller+15} sample of early-type galaxies (a green line shows
  the best power-law fit $\langle L_X/L_{\rm edd}\rangle \propto
  M_{\bullet}^{\alpha}$, with $\alpha = -0.2$).  The left panel is
  calculated assuming a constant radiative efficiency
  $\epsilon_X=10^{-4} (\epsilon_{\rm bol}/0.1)$, while the right hand
  panel assumes $\epsilon_X= (\epsilon_{\rm
    bol}/0.1)(\Mdot/\MdotEdd)$, as predicted by ADAF models (e.g.,
  \citealt{Narayan&Yi95}).  Shown for comparison are the X-ray
  luminosities calculated for the maximum thermally-stable accretion
  rate ({\it orange line}; eq.~[\ref{eq:Mdotmax}]); the SN
  Ia-regulated accretion rate ({\it teal line};
  eq.~[\ref{eq:eddr_Ia}]), and the Compton heating-regulated accretion
  rate ({\it pink line}; eq.~[\ref{eq:MdotCa}]), again all calculated
  for the average SFH corresponding to each SMBH
  mass.}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} Average nuclear X-ray luminosity, $\langle
  L_X \rangle = \epsilon_X \Mdot c^2$, as a function of SMBH mass.
  Green lines show our prediction in the case of heating due to the
  average SFH for galaxies corresponding to each black hole mass
  (Fig.~\ref{fig:bh_growth}), calculated using a power-law fit for the
  relationship $\Gamma(M_{\bullet})$ derived from the
  \citet{LauerFaber+:2007a} sample.  Shown for comparison are the
  measurements ({\it black stars}) and upper limits ({\it gray 
    triangles}) for $L_X/L_{\rm edd}$ values, from the
  \citet{Miller+15} sample of early-type galaxies (a black line shows
  the best power-law fit $\langle L_X/L_{\rm edd}\rangle \propto
  M_{\bullet}^{\alpha}$, with $\alpha = -0.2$).  The left panel is
  calculated assuming a constant radiative efficiency
  $\epsilon_X=10^{-4} (\epsilon_{\rm bol}/0.1)$, while the right hand
  panel assumes $\epsilon_X= (\epsilon_{\rm
    bol}/0.1)(\Mdot/\MdotEdd)$, as predicted by ADAF models (e.g.,
  \citealt{Narayan&Yi95}).  Shown for comparison are the X-ray
  luminosities calculated for the maximum thermally-stable accretion
  rate ({\it dashed orange line}; eq.~[\ref{eq:Mdotmax}]); the SN
  Ia-regulated accretion rate ({\it dashed teal line};
  eq.~[\ref{eq:eddr_Ia}]), and the Compton heating-regulated accretion
  rate ({\it dashed pink line}; eq.~[\ref{eq:MdotCa}]), again all
  calculated for the average SFH corresponding to each SMBH mass.}
\end{figure*}
